---
title: "PDL(Cluster)"
author: "Vivek"
date: "20/Jun/2019"
output:
  html_document:
    df_print: paged
---

# K-means Clustering using Product Detail List Dataset

## Importing Required Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(readxl)
library(cluster)
library(factoextra)
library(fpc)
library(tidyverse)
library(knitr)
library(psych)
```


### Importing Required Dataset

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
z1<-read_excel("F:/DATA ANALYSIS/PROJECT/VAYA SALON/vaya.xlsx", 
    sheet = "Product Detail List", col_types = c("text", 
               "numeric", "text", "text", "text", 
               "text", "text", "text", "numeric", 
               "numeric", "numeric", "numeric", 
               "numeric", "numeric", "text", "text", 
               "text", "text"))
```



### Removing unnecessary variables
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
names(z1)
z2<-subset(z1,select=c(On_HandQty,Cost,Retail_Price))
```





#### Removing Skewness in cost and Retail price
##### Distribution of Cost
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(z1,aes(Cost))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Cost)),color="red")+
  geom_vline(aes(xintercept=median(Cost)),color="green")+
  labs(x="Cost",y="Density",title="Distribution of cost")

#Removing Skewness

for(i in 1:2){
z2$Cost<-sqrt(z2$Cost)
i+1
}
ggplot(z2,aes(Cost))+
  theme_minimal()+
  geom_density(fill="lightblue",color="blue")+
  geom_vline(aes(xintercept=mean(Cost)),color="red")+
  geom_vline(aes(xintercept=median(Cost)),color="green")+
  labs(x="Square root of Cost",y="Density",
       title="Distribution of Cost after removing Skewness")
```





#### Distribution of Retail Price
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(z1,aes(Retail_Price))+
  theme_minimal()+
  geom_density(fill="lightblue",color="blue")+
  geom_vline(aes(xintercept=mean(Retail_Price)),color="red")+
  labs(x="Retail Price",y="Density",title="Distribution of Retail Price")

#Removing Skewness
for(i in 1:3){
z2$Retail_Price<-sqrt(z2$Retail_Price)
i+1
}

ggplot(z2,aes(Retail_Price))+
  theme_minimal()+
  geom_density(fill="lightblue",color="blue")+
  geom_vline(aes(xintercept=mean(Retail_Price)),color="red")+
  labs(x="Retail Price",y="Density",
       title="Distribution of Retail Price after removing Skewness")
```


```{r}
kable(describe(z2))
```




# Applying K-means Clustering
### Determining number of clusters
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}

wss<-0

for(i in 1:15){
  wss[i]<-sum(kmeans(z2,centers = i)$withinss)
}
plot(1:15,wss,type="b",col="blue")
wss[3]-wss[4]
wss[4]-wss[5]
wss[5]-wss[6]
```




### Clustering with 4 clusters
```{r}

z3<-scale(z2)
clus<-kmeans(z3,4,iter.max = 20,nstart = 25)
```



#### Within Sum of Squares of Clusters
```{r}
clus$withinss
```



#### Between Sum of Squares of Clusters
```{r}
clus$betweenss
```



#### Size of Every Cluster
```{r}
clus$size
```




### Silhouette coefficient
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
diss<-daisy(z2)
diss1<-diss^2
silcof<-silhouette(clus$cluster,diss1)
plot(silcof,col="red")
```



### Plotting
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
fviz_cluster(clus,z3,
             ellipse = TRUE,
             geom="point",
             repel = TRUE,
             show.clust.cent = TRUE,
             ggtheme = theme_minimal())
```

#### Creating a new Data Frame with Cluster Variable
```{r}
z4<-data.frame(z1,Cluster=clus$cluster)
```




#write.csv(z4,"F:\\DATA #ANALYSIS\\PROJECT\\VAYASALON\\Modelling\\PDL(CLUSTERS).csv")




### Loading new Data Set for Analysis on Clusters formed
```{r}
cluster<-read.csv("F:\\DATA ANALYSIS\\PROJECT\\VAYA SALON\\Modelling\\PDL(CLUSTERS).csv")
cluster$Cluster<-as.factor(cluster$Cluster)
```




#### Size of every cluster
```{r}
m1<-cluster%>%
  select(Cluster)%>%
  group_by(Cluster)%>%
  summarise(size=n())%>%
  arrange(size)
kable(m1)
```



#### Values per Clusters
```{r}
m2<-cluster%>%
  select(Cost,Retail_Price,On_HandQty,Cluster)%>%
  group_by(Cluster)%>%
  summarise(Average_OnHandQty=mean(On_HandQty),Average_Cost=mean(Cost),
            Average_Retail_Price=mean(Retail_Price))
kable(m2)  
```


##### Average On Hand Quantity in every Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m2,aes(Cluster,Average_OnHandQty,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Average_OnHandQty))+
  geom_text(aes(label=Average_OnHandQty),hjust=-0.3)+
  labs(x="Clusters",y="Average on hand quantity",
       title="Average on hand quantity per Clusters")
```



##### Average Cost per Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m2,aes(Cluster,Average_Cost,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Average_Cost))+
  geom_text(aes(label=Average_Cost),hjust=-0.3)+
  labs(x="Clusters",y="Average Cost",
       title="Average Cost per Clusters")
```



##### Average Retail Price Per Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m2,aes(Cluster,Average_Retail_Price,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Average_Retail_Price))+
  geom_text(aes(label=Average_Retail_Price),hjust=-0.3)+
  labs(x="Clusters",y="Average Retail Price",
       title="Average Retail Price per Clusters")
```