---
title: "Ticket Detail Summary"
author: "Vivek"
date: 20/Jun/2019
output: word_document
---

# K-means Clustering using Ticket Detail Summary Dataset

#### Importing Required Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(readxl)
library(cluster)
library(factoextra)
library(fpc)
library(tidyverse)
library(knitr)
```



#### Importing Dataset
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
z1<-read_excel("F:/DATA ANALYSIS/PROJECT/VAYA SALON/vaya.xlsx", 
               sheet = "Ticket Detail Summary", col_types = c("text", 
                                                              "numeric", "numeric", "text", "text", 
                                                              "text", "numeric", "numeric", "numeric", 
                                                              "numeric", "numeric", "numeric", 
                                                              "numeric", "text", "numeric"))
```



#### Removing unnecssary Variables
```{r}
kable(names(z1))

z2<-subset(z1,select=c(Total_Sales,Other_Sales,Service_Sales,Product_Sales,Discount))

kable(names(z2))
```



### Tunning variables for Modelling
#### Total Sales
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
z2$Total_Sales<-ifelse(z2$Total_Sales<0,0,z2$Total_Sales)

ggplot(z2,aes(Total_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Total_Sales)),color="red")+
  labs(x="Total Sales",y="Density",title="Distribution of Total Sales")

z2$Total_Sales<-sqrt(z2$Total_Sales)

ggplot(z2,aes(Total_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Total_Sales)),color="red")+
  labs(x="Total Sales",y="Density",title="Distribution of Square Root of Total Sales")
```



#### Other_Sales
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(z2,aes(Other_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Other_Sales)),color="red")+
  labs(x="Other Sales",y="Density",title="Distribution of Other Sales")

z2$Other_Sales<-sqrt(z2$Other_Sales)

ggplot(z2,aes(Other_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Other_Sales)),color="red")+
  labs(x="Other Sales",y="Density",title="Distribution of Sqaure Root of Other Sales")
```




#### Service Sales
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(z2,aes(Service_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Service_Sales)),color="red")+
  labs(x="Service Sales",y="Density",title="Distribution of Service Sales")

for(i in 1:2){
z2$Service_Sales<-sqrt(z2$Service_Sales)
i+1
}

ggplot(z2,aes(Service_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Service_Sales)),color="red")+
  labs(x="Service Sales",y="Density",title="Distribution of Service Sales")
```




#### Product Sales
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
z2$Product_Sales<-ifelse(z2$Product_Sales<0,0,z2$Product_Sales)

ggplot(z2,aes(Product_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Product_Sales)),color="red")+
  labs(x="Product Sales",y="Density",title="Distribution of Product Sales")

z2$Product_Sales<-sqrt(z2$Product_Sales)

ggplot(z2,aes(Product_Sales))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Product_Sales)),color="red")+
  labs(x="Product Sales",y="Density",title="Distribution of Product Sales")
```



#### Discount
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(z2,aes(Discount))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Discount)),color="red")+
  labs(x="Discount",y="Density",title="Distribution of Discount")

z2$Discount<-sqrt(z2$Discount)

ggplot(z2,aes(Discount))+
  theme_minimal()+
  geom_density(color="blue",fill="lightblue")+
  geom_vline(aes(xintercept=mean(Discount)),color="red")+
  labs(x="Discount",y="Density",title="Distribution of Discount")
```




### Detrmining number of clusters
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
set.seed(123)
#Calculating within_sum_of_squares of each cluster
wss<-0
for(i in 1:15){
  wss[i]<-sum(kmeans(z2,centers=i)$withinss)
}
#Determining number of clusters using Elbow Method
plot(1:15,wss,type="b",col="blue")
wss[3]-wss[4]
wss[4]-wss[5]
wss[5]-wss[6]
```



### Clustering with 4 clusters
```{r}
#Scaling Dataset for equal weights
z3<-scale(z2)
#Applying K-Means clustering with 20 iterations
clus<-kmeans(z3,4,iter.max = 20,nstart = 25)
```



##### Within Sum of Squares of Clusters
```{r}
clus$withinss
```




##### Between Sum of Sqaures of Clusters
```{r}
clus$betweenss
```




##### Size of Clusters
```{r}
clus$size
```




### Silhouette Coefficient
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
diss<-daisy(z3)
diss1<-diss^2
silcof<-silhouette(clus$cluster,diss1)
plot(silcof,col="lightblue")
```



#### Plotting
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
fviz_cluster(clus,z3,
             ellipse = TRUE,
             geom="point",
             repel = TRUE,
             show.clust.cent = TRUE,
             ggtheme = theme_minimal())
```




##### Creating a new dataframe for cluster exploration
```{r}
z4<-data.frame(z1,Cluster=clus$cluster)
z5<-data.frame(z2,Cluster=clus$cluster)
```
#write.csv(z4,"F:\\DATA ANALYSIS\\PROJECT\\VAYA #SALON\\Modelling\\TDS(CLUSTER).csv")



### Exploring Patterns in Clusters
```{r}
z5$Cluster<-as.factor(z5$Cluster)

m1<-z5%>%
  select(Total_Sales,Other_Sales,
         Service_Sales,Product_Sales,
         Discount,Cluster)%>%
  group_by(Cluster)%>%
  summarise(Avg_Total_Sales=mean(Total_Sales),
            Avg_Other_Sales=mean(Other_Sales),
            Avg_Service_Sales=mean(Service_Sales),
            Avg_Product_Sales=mean(Product_Sales),
            Avg_Discount=mean(Discount))
```



#### Rounding off Values
```{r}
m1$Avg_Total_Sales<-round(m1$Avg_Total_Sales,digits = 2)
m1$Avg_Other_Sales<-round(m1$Avg_Other_Sales,digits = 2)
m1$Avg_Service_Sales<-round(m1$Avg_Service_Sales,digits = 2)
m1$Avg_Product_Sales<-round(m1$Avg_Product_Sales,digits = 2)
m1$Avg_Discount<-round(m1$Avg_Discount,digits = 2)
kable(m1)
```



### Average Total Sales Per Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m1,aes(Cluster,Avg_Total_Sales,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Avg_Total_Sales))+
  geom_text(aes(label=Avg_Total_Sales),hjust=-0.3)+
  labs(x="Clusters",y="Average Total Sales",
       title="Average Total Sales per Cluster")
```



### Average Other Sales per Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m1,aes(Cluster,Avg_Other_Sales,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Avg_Other_Sales))+
  geom_text(aes(label=Avg_Other_Sales),hjust=-0.3)+
  labs(x="Clusters",y="Average Other Sales",
       title="Average Other Sales per Cluster")
```



### Average Service Sales per Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m1,aes(Cluster,Avg_Service_Sales,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Avg_Service_Sales))+
  geom_text(aes(label=Avg_Service_Sales),hjust=-0.3)+
  labs(x="Clusters",y="Average Service Sales",
       title="Average Service Sales per Cluster")
```



### Average Product Sales per Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m1,aes(Cluster,Avg_Product_Sales,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Avg_Product_Sales))+
  geom_text(aes(label=Avg_Product_Sales),hjust=-0.3)+
  labs(x="Clusters",y="Average Product Sales",
       title="Average Product Sales per Cluster")
```



### Average Discount per Cluster
```{r fig.height=10, fig.width=14, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(m1,aes(Cluster,Avg_Discount,color=Cluster))+
  theme_minimal()+
  geom_point(size=5)+
  geom_segment(aes(x=Cluster,
                   y=0,
                   xend=Cluster,
                   yend=Avg_Discount))+
  geom_text(aes(label=Avg_Discount),hjust=-0.3)+
  labs(x="Clusters",y="Average Discount",
       title="Average Discount per Cluster")
```
